\plaintitle

### 2016-09-21 drafts/labor/complexity.tex
relationships.tex

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} are amenable to piecework.}
% \msb{I think a reader wouldn't understand why that claim is relevant.
% Let's invert it, something like how
% the researchers point out that
% only certain kinds of organizations can effectively make use of piecework.}
\citeauthor{Brown01041990} discusses the organizational factors necessary for piecework to thrive,
arguing that piecework
``\dots~ is less likely in jobs with
a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}
% \msb{that's confusing, is incentive pay the same as piecework?
% can you cut the first part of the quote and
% give us the noun instead of forcing us to figure it out?}.
\citeauthor{10.2307/23702539} adds further, that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.
Together, \citeauthor{10.2307/23702539} and \citeauthor{Brown01041990}
make a persuasive argument that piecework is limited in complexity by
the capacity to endure managerial overhead while transitioning to a new system.
\msb{wait, wasn't that in a previous paragraph?
that should be joined with the managerial overhead text above}
\ali{I'm trying to make this argument that \cite{10.2307/23702539} is making two claims;
the first is that there are limits on doing hard, ``difficult--to--observe'' work,
and the second is that the cost propagates up to management,
putting limits on who can run piecework systems.
So\dots\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Rewrite\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Refactor\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Drop

>>>>

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} are amenable to piecework.}
% \msb{I think a reader wouldn't understand why that claim is relevant.
% Let's invert it, something like how
% the researchers point out that
% only certain kinds of organizations can effectively make use of piecework.}
\citeauthor{Brown01041990} discusses the organizational factors necessary for piecework to thrive,
arguing that piecework
``\dots~ is less likely in jobs with
a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{SJOE:SJOE371} points out the phenomenon here as a market effect:
``\dots~in an environment with multi--tasking,
pay schemes based on tightly specified performance may \textit{induce workers
to neglect tasks} that are less easy to measure [emphasis added]''
\cite{SJOE:SJOE371}.
% \msb{that's confusing, is incentive pay the same as piecework?
% can you cut the first part of the quote and
% give us the noun instead of forcing us to figure it out?}.
\citeauthor{10.2307/23702539} argues that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.
Together, \citeauthor{10.2307/23702539} and \citeauthor{Brown01041990}
make a persuasive argument that piecework is limited in complexity by
the capacity to endure managerial overhead while transitioning to a new system.
\msb{wait, wasn't that in a previous paragraph?
that should be joined with the managerial overhead text above}
\ali{I'm trying to make this argument that \cite{10.2307/23702539} is making two claims;
the first is that there are limits on doing hard, ``difficult--to--observe'' work,
and the second is that the cost propagates up to management,
putting limits on who can run piecework systems.
So\dots\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Rewrite\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Refactor\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Drop

### 2016-09-21 drafts/labor/relationships.tex
relationships.tex

Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \textit{Turkopticon}, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
designing \textit{Dynamo} to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

@@

\ali{What do I want to do/say here? I think I want to point to point out that
\dots~I dunno. I'll review the \citetitle{american1921problem} book and maybe some other stuff}

\subsubsubsection{\whatchanged}
\topic{The differences between crowd workers and pieceworkers seem defined largely by
the differences in the places of work.}
Whereas it arguably became inevitable that workers would have a place to
meet, discuss, and collaborate
when they began sharing places of work,
online spaces make it much harder to do so.
Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
without any affiliation with
--- or even knowledge of ---
communities of peers
\ali{multiple citations that labor unions came out of factories here}
\cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

While the historical management of workers had to be done by hiring a foreman,
who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers,
the foreman of the \nth{20} century has largely been replaced
by the algorithm of the \nth{21} century
\cite{uberAlgorithm}.
The result of this change is that the agents managing work are now
cold and logical, if unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive are stopped,
some implementations of these approaches
(\cite[see][]{MaliciousCrowdworkersGadiraju}
only seem to antagonize workers
\cite{le2010ensuring,MaliciousCrowdworkersGadiraju}.

@@

>>>>

Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \TO, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
designing \DO~to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

@@

The driving force of American labor advocacy organizations was to get piecework railroad workers
to identify
``not only as railroad employees but also as members of the larger life of the community''
\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others argued,
would facilitate collective action and perhaps collective governance
\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} had contributed to this sense of shared struggle and endurance
by the time \citetitle{american1921problem} was published
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked
\cite{riisOtherSideLives}.

% This can also foreshadow crowd sourcing efforts like
% \TO~and \DO.

\subsubsubsection{\whatchanged}
\topic{The differences between crowd workers and pieceworkers seem defined largely by
the differences in the places of work.}
Whereas it arguably became inevitable that workers would have a place to
meet, discuss, and collaborate
when they began sharing places of work,
online spaces make it much harder to do so.
Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
without any affiliation with
--- or even knowledge of ---
communities of peers
% \ali{multiple citations that labor unions came out of factories here}
\cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

\topic{We further find the sources of differences between crowd work and piecework
in the nature of the relationship between workers and requesters
--- or rather, the lack thereof.}
While historically the management of workers had to be done through a foreman
(who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers),
the foreman of the \nth{20} century has largely been replaced
by algorithms of the \nth{21} century
\cite{uberAlgorithm}.
The result of this change is that the agents managing work are now
cold and logical, if unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive are stopped,
some implementations of these approaches
only seem to antagonize workers \ali{shots fired}
\cite{le2010ensuring,MaliciousCrowdworkersGadiraju}.
% We've known for decades that workers prefer human management 
\citeauthor{10.2307/2555446} told us more than 30 years ago
--- in \citeyear{10.2307/2555446} --- that
``\dots~when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''
\cite{10.2307/2555446}.
\ali{here's an idea. feel free to push back or revise or something:\\
``Should we be surprised that
management approaches we've known to
frustrate pieceworkers since \citeyear{10.2307/2555446}
would only aggravate crowd workers in many of the same ways?''}

@@

\topic{The research on piecework still offers to guide us on perhaps the most rudimentary aspects of worker management}
\citeauthor{10.2307/2555446} drew a dichotomous line between
``defective (simple, observable) output measures'' and
``a manager's subjective judgment'',
but such a dichotomy need not necessarily represent our work management styles
\cite{10.2307/2555446}.
We can develop tools that better inform humans, rather than
(perhaps futilely) attempt to delegate all worker management to machines.
This is an area we should pursue, but haven't yet.
If the literature on piecework is to be believed,
more considerate \textit{human} management may resolve
many of the tensions we've discovered among among crowd workers.
